Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-19 article/draft.tex
start to write discussion part 3

{\bf A need for more consistent policies.}
{\color{brown} why a difference between Infowars and The beauty of life? }

It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
To illustrate, YouTube explicitly states
\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.}
that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
$Classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech. 
Nevertheless, tackling online misinformation is an active area of research and adapted interventions might be required to avoid undesired effects. 
Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation. 
We invite the reader to see Rogers (2020)~\cite{rogers2020} for an excellent overview about de-platforming and see Robins-Early (2019)~\cite{huffpost} for a news article about Alex Jones's account suspension on Facebook.

{\color{brown} Recommendation: inform about sources, example inform users that this account has shared x failed fact-checks over a x-months period.}

@@

%		\item[${\color{green}\surd}$] Make point about the communication of platforms for their policy: 4R of YouTube, RRI of Facebook. Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).

@@

		%Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.

		%User side: psychological effects (Pennycook, etc.), multi-platforms, indirect effects, strategies... business model

>>>>

{\bf A need for more consistent and adapted policies.}
Both Infowars and The Beauty of Life domains are considered as spreading misinformation (they are both on the Iffy+ list\footnote{https://iffy.news/iffy-plus/}), and violated Facebook's guidelines (incitation to violence and coordinated unauthentic behavior). 
Yet one's distribution was reduced for only half a year, while the other one's links cannot be shared anymore on Facebook since the end of 2019, and it is not clear why such double standard was applied on these comparable websites.
Misinformation on the web is a problem that is increasingly discussed since the 2016 American elections, and in the years that followed, the platforms may have decided manually and on a case-by-case basis which action to enforce.
It is also possible that platforms usually follow specific rules on how to fight misinformation, but that sometimes the sudden mediatization of specific events leads them to take exceptional actions, such as with the Capitol riots and Trump's suspension from Facebook, Twitter and YouTube.

@@

It is likely that most interventions related to misinformation correspond to interventions that were designed for other policy areas or aim violations that fall into other categories cited in the platforms' guidelines.
To illustrate, YouTube explicitly states
\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.}
that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
$Classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech, but tackling online misinformation might need adapted interventions.
Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation (Rogers (2020)~\cite{rogers2020}, Robins-Early (2019)~\cite{huffpost}).

{\color{brown} Recommendation to fight misinformation: inform about sources, example inform users that this account has shared x failed fact-checks over a x-months period.}

{\color{brown} Tackling online misinformation is an active area of research and adapted interventions might be required to avoid undesired effects. 
psychological and indirect effects (Pennycook, etc.). 
How labels can work against their intent.}

{\color{brown} Make point about how the three platforms communicate differently about their policies. 
Need for a consistent policy for all, but this will surely come only when a law against misinformation is issued. 
Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. 
Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. 
In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).}

@@

%User side: indirect effects, strategies... business model
